RationalGRL: A Framework for Argumentation and Goal Modeling

### 2017-10-08 formalframework.tex

\subsection{Constructing GRL models}
\label{sect:rationalGRL-GRL}
\todo{F}{F,M}{It would be good to have a formal definition of how to construct models given an argumentation framework. If we define a model M at the start of this section, this should be fairly easy.}

>>>>

\subsection{Constructing GRL models}
\label{sect:rationalGRL-GRL}
\todo{F}{F,M}{Dit is snel getypt, moet nog checken of het klopt.}

\begin{definition}[RationalGRL model] A RationalGRL model $\mathcal{R}$ is an argumentation framework $AF=(Args,Att)$ where all arguments in $Args$ and attacks in $Att$ are based on algorithm X-XX.  
\end{definition}

\begin{definition}[GRL model] A GRL model $\mathcal{M}$ based on a RationalGRL model $\mathcal{R}$ is the preferred extension of $\mathcal{R}$.  
\end{definition}
=======
\todo{F}{F,M}{It would be good to have a formal definition of how to construct models given an argumentation framework. If we define a model M at the start of this section, this should be fairly easy.}
